\section{Software development (R extension packages)}
\cvitem{mefa, mefa4}{packages for multivariate data handling, using sparse matrices for big data problems.}
\cvitem{dclone, dcmle}{low level interface for maximum likelihood methods using data cloning and Bayesian MCMC with support for JAGS, WinBUGS, OpenBUGS and STAN. Parallel computing features for computational performance.}
\cvitem{detect}{zero inflated models for single visit data when the probability of detection is less than one. Provides hands-on formula interface with inferences based on numerical optimization and data cloning (with M.~Moreno \& S.~Lele).}
\cvitem{ResourceSelection}{resource selection (probability) function estimation (with J.~Keim \& S.~Lele).}
\cvitem{PVAClone}{likelihood based population viability analysis in the presence of observation error and missing data. Fit, compare, predict, and forecast various growth model types using data cloning (with K.~Nadeem).}
\cvitem{vegan}{a collaborative project for community ecology methods in R, with J.~Oksanen as lead developer. Contributing to the package with diversity analysis and community nullmodels.}
\cvitem{adegenet, epiR, plotrix, pbapply}{miscellaneous contributions.}

%\section{Other software skills}
%\cvitem{Database management}{Micrososft Access, SQL}
%\cvitem{Version control}{Subversion, Git, MS Sharepoint}
%\cvitem{Bayesian graphical modeling software}{JAGS, OpenBUGS, WinBUGS, STAN}
%\cvitem{Markup languages}{HTML, LaTeX}
%\cvitem{Computing}{Julia}

\section{Language skills}
\cvitem{Hungarian}{mother tongue}
\cvitem{English}{proficient, specialist degree in scientific translation, IELTS Band Score 7.5}
\cvitem{German, Russian, Latin}{basic}

