\section{Textbook development} % ------------------------

\cvlistitem{\psolymos~(in press). Puhatest\"{u}ek (Mollusca) t\"{o}rzse [Phylum Mollusca]. In: R\'{o}zsa, L., Papp, L.~and Varga, Z.~(eds.): \emph{Zootaxon\'{o}mia [Zootaxonomy]}. Kossuth Press, Budapest.}

\cvlistitem{Half-finished textbook on \emph{Multivariate methods in ecology with R} by \psolymos, Oksanen, J.~and T\'{o}thm\'{e}r\'{e}sz, B.~(under contract with Springer, UseR! series).}

\cvlistitem{Started developing the book \emph{A primer on data cloning: hierarchical models made easy} by \psolymos~and S.~Lele (Chapman \& Hall invited us to submit a book proposal, we are working on the first 5 chapters).}

\section{Approach to graduate supervision} % ------------------------

I have adopted an open-door policy with my students and I usually met them as frequently as it was required by the actual activities (e.g. help with identification, preparing for conferences, writing papers). When a student was located at a different institution, I met them less frequently and we communicated via phone and email.
\vspace{0.5pc}

My students are successful in life, but not all have pursued academic carriers. The feedback I have received from my supervised students was positive, and they appreciated that I demanded their best efforts. I think the most important feedback and help students should receive from their supervisor is how to identify short and long term goals, how to prioritize tasks and objectives strategically, and how to maintain a vision of the `big-picture' during the everyday work.

\section{Evidence of professional development} % ------------------------

\cvlistitem{I graduated as biologist and biology teacher (Appendix). During my studies towards the teaching degree, I learnt pedagogical and didactical subjects, and did practice teaching for one semester in two high schools. This period taught me to remain calm, considerate, and fair in challenging situations.}

\cvlistitem{I participated on a one-day workshop ``Talking to people'' by Lorne Fitch (Edmonton AB, September 2013).}

\section{Teaching related service} % ------------------------

\cvlistitem{2012--: founding member of the `Edmonton R User Group' (ERUG).}

\cvlistitem{2005--2007: jury member, Scientific Student Competition, Biology Section, E\"{o}tv\"{o}s University, Budapest, Hungary}

