\documentclass[11pt,letterpaper,roman]{moderncv}

\usepackage{SolymosCV}

\begin{document}

\makelettertitle

I am applying for the Tenure Track Faculty Position (116308) in Terrestrial Ecology in the Department of Biological Sciences at the Simon Fraser University. I want to further my professional development through increased academic collaboration, co-supervision of graduate students, and teaching of advanced statistical methods. Please accept this letter, curriculum vit\ae{}, and sponsor letter from Associate Professor Dr.~Erin Bayne, Department of Biological Sciences as my formal application.
\vspace{0.1pc}

I am an ecologist whose research focus is developing and applying state-of-the-art quantitative techniques for big data sets to better inform conservation and management of biodiversity over large spatial scales. I am well versed in field ecology, theoretical ecology, and statistical techniques. My strength is in linking statistical models to field data through ecological theory. As software developer, I write computer programs when currently available numerical tools do not allow meaningful linking of models to data. I am a senior developer of one of the most widely used R packages among ecologists, the `vegan' package for community ecology, and maintainer of several other more specific packages for data management, hierarchical modeling, presence-only and animal movement data, population viability analysis, and correcting for detection error. In 2012, I received the Young Biostatistician of the Year award by the Hungarian Society for Clinical Biostatistics.  More recently, I gave an invited talk at the 2013 Annual Meeting of the Statistical Society of Canada and the 2014 Joint Ornithologist (AOU/COS/SCO) Meeting.
\vspace{0.1pc}

I started my research on community ecology and conservation of lands snails in Hungary as a graduate student and in 2006 I defended my PhD Thesis on conservation prioritization of land snails in Hungary based on museum records. I was the Hungarian coordinator for the international citizen science program Evolution MegaLab. I moved to the University of Alberta in 2008 as a postdoc with Dr.~Subhash Lele (Dept.~of Mathematical and Statistical Sciences) to work on hierarchical and mixture models. 
\vspace{0.1pc}

Since 2009 I have been working as a Statistical Ecologist for the Alberta Biodiversity Monitoring Institute (ABMI). In 2010, I also started working part time for the Boreal Avian Modeling Project (BAM). At both ABMI and BAM, my main role has been developing numerical techniques to study the effects of human disturbance on biodiversity in the presence of observation error. As demonstrated by my recent publications and R packages, I have been working in a highly collaborative environment that allows me to rapidly engage in ongoing interdisciplinary research by developing new algorithms for data management and analysis.
\vspace{0.1pc}

%I already am interacting with students in the Department of Biological Sciences, especially in the Boutin \& Bayne labs, helping with statistical analysis and more recently as committee member for a grad student with Dr.~Erin Bayne. Based on my previous teaching and supervising experience in Hungary, I am well positioned to train and co-supervise students working on data analysis problems on a wide variety of topics.
%\vspace{0.1pc}

%My future work will involve the development of statistical methodologies for acoustic monitoring and camera traps through a CRD grant by Boutin \& Bayne labs, estimating population trends and accounting for errors in predictor variables when modeling and predicting the distribution and abundance of species. I also plan to apply for research grants to advance these topics, which would provide financial support for graduate students. These research goals are shared by the Boutin \& Bayne lab and ABMI, and will further advance cooperation among these groups. 
%\vspace{0.1pc}

%I am also planning to develop a course on big data management and analysis using ABMI and other large-scale datasets as practical examples. Such a course would fit well into the CREATE EI graduate program headed by Dr.~Stan Boutin and would facilitate uptake of the data collected by ABMI. I am particularly interested in co-supervising and acting as a committee member for graduate students within the department. I have very specialized knowledge and experience with large biodiversity data sets and feel that teaching a course at the post-secondary level that focuses on recent advances in statistical ecology would strongly benefit myself and the programs at the department.
%\vspace{0.1pc}

I look forward to hearing from the Search Committee regarding my application for Faculty Position in the Department of Biological Sciences at the Simon Fraser University.
\vspace{0.1pc}

%\makeletterclosing
\makeletterclosingsigned
\vfill%
\formatenclosed{Attached:}\\%
%\formatenclosure{R\'{e}sum\'{e}}\\%
\formatenclosure{Curriculum vit\ae{}}\\%
\formatenclosure{Concise research statement}\\%
\formatenclosure{Teaching experience and philosophy}\\%
%\formatenclosure{Sponsor letter sent separately by Dr.~Bayne}\\%
%\formatenclosure{Research and teaching interests}\\%
%\formatenclosure{List of publications}\\%
%\formatenclosure{Recent publications}\\%

\end{document}
